---
title: "Character Manipulation"
author: "John Cruz"
date: "2023-02-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Required libraries

```{r library, message=FALSE, warning=FALSE}
library(tidyverse)
library(rvest)
```

---

## Question 1
Using the 173 majors listed in fivethirtyeight.com’s College Majors [dataset](https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/), provide code that identifies the majors that contain either "DATA" or "STATISTICS"

```{r website-table, warning=FALSE, message=FALSE}
url <- "https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv"
df <- read_csv(url)
```

### Method 1

```{r method-1, warning=FALSE, message=FALSE}
word_search <- list("statistics", "data")
majors_data_stats <- list()

for (word in word_search){
  majors_data_stats <- append(majors_data_stats, grep(word, df$Major, ignore.case = TRUE, value = TRUE))
}

print(majors_data_stats)
```
### Method 2

```{r method-2, warning=FALSE, message=FALSE}
df %>%
  filter(str_detect(Major, regex("statistics|data", ignore_case = TRUE)))
```

---

## Question 2
Write code that transforms the data below:

[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"

[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  

[9] "elderberry"   "lime"         "lychee"       "mulberry"    

[13] "olive"        "salal berry"

Into a format like this:

c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")

``` {r transform-string, warning=FALSE}

start_str <- '[1] "bell pepper" "bilberry"   "blackberry"  "blood orange"
[5] "blueberry"  "cantaloupe"  "chili pepper" "cloudberry"
[9] "elderberry"  "lime"     "lychee"    "mulberry"
[13] "olive"    "salal berry"'

patterns <- c('\\[' = '', '[0-9]'='', '\\]'='', '\n'='')
remove_chars <- str_replace_all(start_str, patterns)
remove_backslash <- str_split(remove_chars, '\\"')
remove_quotes <- str_split(remove_backslash, '\\"')

df_words <- as.data.frame(str_extract_all(remove_quotes, "(\"\\w*[:blank:]?\\w*\")+", simplify=TRUE))
df_words <- as.data.frame(df_words[!apply(df_words, 1, function(x) any(x=="")),])

df_t <- transpose(df_words)
df_t <- as.data.frame(lapply(df_t, unlist))

df_final <- df_t %>% filter(grepl('[a-zA-Z]', df_t[ , 1]))

update_string <- ''

for (word in df_final){
  update_string <- paste(update_string, word, collapse = ', ')
}

update_string <- paste0('c(', update_string) %>%
  paste0(update_string, ')')

writeLines(update_string)

```

---

## Question 3
Describe, in words, what these expressions will match:

(.)\1\1
Same character repeated three times

"(.)(.)\\2\\1"
Two consecutive characters that is backwards

(..)\1
Two same characters repeated

"(.).\\1.\\1"
Every other character should be repeated

"(.)(.)(.).*\\3\\2\\1"
Three characters separated by any number of different repeated characters including none, then the three characters backwards.
---

## Question 4
Construct regular expressions to match words that:

Start and end with the same character.
"^(.)((.*\\1)|1?)"

Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)
"([A-Za-z][A-Za-z]).*\\1"

Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)
"([A-Za-z]).*\\1.*\\1"
