---
title: "Character Manipulation"
author: "John Cruz"
date: "2023-02-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Required libraries

```{r library, message=FALSE, warning=FALSE}
library(tidyverse)
library(rvest)
```

---

## Question 1
Using the 173 majors listed in fivethirtyeight.com’s College Majors [dataset](https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/), provide code that identifies the majors that contain either "DATA" or "STATISTICS"

```{r website-table, warning=FALSE, message=FALSE}
url <- "https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv"
df <- read_csv(url)
```

### Method 1

```{r method-1, warning=FALSE, message=FALSE}
word_search <- list("statistics", "data")
majors_data_stats <- list()

for (word in word_search){
  majors_data_stats <- append(majors_data_stats, grep(word, df$Major, ignore.case = TRUE, value = TRUE))
}

print(majors_data_stats)
```
### Method 2

```{r method-2, warning=FALSE, message=FALSE}
df %>%
  filter(str_detect(Major, regex("statistics|data", ignore_case = TRUE)))
```

---

## Question 2
Write code that transforms the data below:

[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"

[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  

[9] "elderberry"   "lime"         "lychee"       "mulberry"    

[13] "olive"        "salal berry"

Into a format like this:

c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")

``` {r transform-string}

start_str <- '[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"

[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  

[9] "elderberry"   "lime"         "lychee"       "mulberry"    

[13] "olive"        "salal berry"'

print(start_str)

remove_chars <- str_replace_all(start_str, '[[0-9][:punct:]\n]', '')
print(remove_chars)

```

---

## Question 3
Describe, in words, what these expressions will match:

(.)\1\1
"(.)(.)\\2\\1"
(..)\1
"(.).\\1.\\1"
"(.)(.)(.).*\\3\\2\\1"

---

## Question 4
Construct regular expressions to match words that:

Start and end with the same character.
Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)
Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)